Convolutional Neural Networks and Volcano Plots: Screening and Prediction of Two-Dimensional Single-Atom Catalysts for CO$_2$ Reduction Reactions

### 2024-01-05 paper/main_sections/5_methods.tex
fix equation/formula format

\subsection{CO$_2$RR pathway}
The C1 production CO$_2$RR pathway, as initially described by Peterson et al. [45] and later confirmed by Jiao et al. [57] for g-C$_3$N$_4$ based SACs, involves the following elementary steps.
Asterisks (*) indicate species adsorbed on the SAC surfaces:
% TODO: check format
% (CO_2+ ^*+H^++e^- □(→┴(          ) )  ^* COOH#(1))
% ( ^* COOH+H^++e^- □(→┴(          ) )  ^* CO+H_2 O#(2))
% ( ^* CO+H^++e^- □(→┴(          ) )  ^* CHO#(3)######)
% ( ^* CHO+H^++e^- □(→┴(          ) )  ^* CH_2 O#(4)##)
% ( ^* CH_2 O+H^++e^- □(→┴(          ) )  ^* OCH_3#(5)#)
% ( ^* OCH_3+H^++e^- □(→┴(          ) )  ^* O+CH_4#(6)#)
% ( ^* O+H^++e^- □(→┴(          ) )  ^* OH#(7)#)
% ( ^* OH+H^++e^- □(→┴(          ) )  ^*+H_2 O#(8)#)

\subsection{Free energy calculations}
Free energies were computed from electronic energies by considering thermal corrections, incorporating normal mode analysis of all degrees of freedom of adsorbates.
The free energy $\textit{G}$ was calculated using the formula:
% TODO: check format
% (G=E+ E_ZPE-TS#(9))
where $\textit{G}$ represents the free energy, $\textit{E}$ denotes electronic energy, $\textit{E}_{\text{ZPE}}$ is the zero-point energy, $\textit{T}$ represents temperature in Kevin, and $\textit{S}$ stands for entropy.
Detailed information regarding these corrections can be found in Supplementary Section 1.3.

The computational hydrogen electrode (CHE) model [45, 58] was employed to introduce potential dependence.
At the reference electrode surface, the reaction
% TODO: check format
% (1/2 H_2(g)   □(↔┴(           )  H^++ e^- )#(10))
is in equilibrium, allowing the calculation of the chemical potential of the electron-proton pair as:
% (μ(H^+)+μ(e^-)=1/2 μ(H_2(g) )-eU#(11))
For the external potential $\textit{U}$ applied, the change in free energy ($\Delta \textit{G}$) was determined using the equation:
% (∆G_n (U)= ∆G_n (U=0)+neU#(12))
Here, $\mu$ represents chemical potential, $\textit{U}$ signifies the external potential applied, $\textit{n}$ represents the number of proton-electron pairs transferred, and $\textit{e}$ denotes the elementary charge.

\subsection{Hybrid descriptor for volcano plots}
Hybrid descriptors incorporate both descriptors within a single equation, enhancing the accuracy of scaling relationship with minimal computational overhead, as demonstrated in Supplementary Figure 10 and Supplementary Table 13.
Comprehensive analyses are presented Supplementary Section 1.5. This leads to the formulation of the scaling relation:
% TODO: check format
% (G_ads Z=k[θ*G_ads CO+(1-θ)*G_ads OH]+c_Z#(13)##)
Here, $\theta$ represents the mixing ratio of the CO descriptor, $\textit{Z}$ denotes any adsorbate, and $\textit{k}$ and $\textit{c}_{Z}$ are adsorbate-specific scaling parameters.
The optimal mixing ratio $\theta$ is determined through iterative exploration across the range, utilizing a step length of 0.01.

Equation 14 could be simplified to a more general form:
% TODO: check format
% (G_ads Z=a_Z G_ads CO+b_Z G_ads OH+c_Z#(14)#)
Here, $a_Z$, $b_Z$, $c_Z$ are adsorbate-specific parameters.

Consequently, the limiting potential $\textit{U}_{L}$ is entirely determined by two descriptors through the following equation:
% TODO: check format
% (U_L=-max⁡{〖ΔG〗_i }/e#(15)#)
Where $\Delta G_{i}$ represents the free energy change of reaction step i.

>>>>

\subsection{CO$_2$RR pathway}
The C1 production CO$_2$RR pathway, as initially described by Peterson et al. [45] and later confirmed by Jiao et al. [57] for g-C$_3$N$_4$ based SACs, involves the following elementary steps.
Asterisks (*) indicate species adsorbed on the SAC surfaces:

\begin{equation*}
\begin{aligned}
\ce{CO2 + H+ + e- &-> \text{*}COOH} \\
\ce{\text{*}COOH + H+ + e- &-> \text{*}CO + H2O} \\
\ce{\text{*}CO + H+ + e- &-> \text{*}CHO} \\
\ce{\text{*}CHO + H+ + e- &-> \text{*}CH2O} \\
\ce{\text{*}CH2O + H+ + e- &-> \text{*}OCH3} \\
\ce{\text{*}OCH3 + H+ + e- &-> \text{*}O + CH4} \\
\ce{\text{*}O + H+ + e- &-> \text{*}OH} \\
\ce{\text{*}OH + H+ + e- &-> \text{*} + H2O}
\end{aligned}
\end{equation*}

\subsection{Free energy calculations}
Free energies were computed from electronic energies by considering thermal corrections, incorporating normal mode analysis of all degrees of freedom of adsorbates.
The free energy $\textit{G}$ was calculated using the formula:
\begin{equation*}
G = E + E_{\text{ZPE}} - TS
\end{equation*}

where $\textit{G}$ represents the free energy, $\textit{E}$ denotes electronic energy, $\textit{E}_{\text{ZPE}}$ is the zero-point energy, $\textit{T}$ represents temperature in Kevin, and $\textit{S}$ stands for entropy.
Detailed information regarding these corrections can be found in Supplementary Section 1.3.

The computational hydrogen electrode (CHE) model [45, 58] was employed to introduce potential dependence.
At the reference electrode surface, the reaction
\begin{equation*}
\ce{1/2H2_{(g)}  <-> H+ + e-}
\end{equation*}
is in equilibrium, allowing the calculation of the chemical potential of the electron-proton pair as:
\begin{equation*}
\mu(H^+) + \mu(e^-) = \frac{1}{2}\mu(H_{2(g)}) - eU
\end{equation*}
For the external potential $\textit{U}$ applied, the change in free energy ($\Delta \textit{G}$) was determined using the equation:
\begin{equation*}
\Delta G_n(U) = \Delta G_n(U=0) + neU
\end{equation*}
Here, $\mu$ represents chemical potential, $\textit{U}$ signifies the external potential applied, $\textit{n}$ represents the number of proton-electron pairs transferred, and $\textit{e}$ denotes the elementary charge.

\subsection{Hybrid descriptor for volcano plots}
Hybrid descriptors incorporate both descriptors within a single equation, enhancing the accuracy of scaling relationship with minimal computational overhead, as demonstrated in Supplementary Figure 10 and Supplementary Table 13.
Comprehensive analyses are presented Supplementary Section 1.5. This leads to the formulation of the scaling relation:
\begin{equation*}
G_{\text{ads}} Z = k[\theta^* G_{\text{ads}} \ce{CO} + (1-\theta^*) G_{\text{ads}} \ce{OH}] + c_Z
\end{equation*}
Here, $\theta$ represents the mixing ratio of the CO descriptor, $\textit{Z}$ denotes any adsorbate, and $\textit{k}$ and $\textit{c}_{Z}$ are adsorbate-specific scaling parameters.
The optimal mixing ratio $\theta$ is determined through iterative exploration across the range, utilizing a step length of 0.01.

Equation 14 could be simplified to a more general form:
\begin{equation*}
G_{\text{ads}} Z = a_Z G_{\text{ads}} \ce{CO} + b_Z G_{\text{ads}} \ce{OH} + c_Z
\end{equation*}
Here, $a_Z$, $b_Z$, $c_Z$ are adsorbate-specific parameters.

Consequently, the limiting potential $\textit{U}_{L}$ is entirely determined by two descriptors through the following equation:
\begin{equation*}
U_L = -\frac{\max\{ \Delta G_i \}}{e}
\end{equation*}
Where $\Delta G_{i}$ represents the free energy change of reaction step i.
